Specific examples

### 2023-03-27 inst/gitbook/_book/dads_manual.tex
Updated numbering in gitbook

\hypertarget{bdalgorithm}{%
\chapter{The birth-death algorithm}\label{bdalgorithm}}

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = sqrt(Sigma^2 * 
##         edge.length), ...)))
## }
## <bytecode: 0x55a505929ed0>
## <environment: namespace:dads>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x55a507be7fe8>
## <environment: namespace:dads>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x55a507c69968>
## <environment: namespace:dads>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) < (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x55a507c7e050>
## <environment: namespace:dads>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\includegraphics{../../../../../../tmp/Rtmp8BGjPN/file97bd69ab2a6.png}

@@

\includegraphics{../../../../../../tmp/Rtmp8BGjPN/file97bd7e5353fb.png}

@@

\includegraphics{../../../../../../tmp/Rtmp8BGjPN/file97bd12f0c3a.png}

@@

\hypertarget{EG_modify_brlen}{%
\chapter{Changing branch length when reaching n taxa}\label{EG_modify_brlen}}

>>>>

\hypertarget{bdalgorithm}{%
\section{The birth-death algorithm}\label{bdalgorithm}}

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = sqrt(Sigma^2 * 
##         edge.length), ...)))
## }
## <bytecode: 0x55e278dc9cd8>
## <environment: namespace:dads>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x55e27b08d1b8>
## <environment: namespace:dads>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x55e27b11eb90>
## <environment: namespace:dads>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) < (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x55e27b127560>
## <environment: namespace:dads>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\includegraphics{../../../../../../tmp/RtmpmEQua5/file9cb853e0a21f.png}

@@

\includegraphics{../../../../../../tmp/RtmpmEQua5/file9cb812c6ed9e.png}

@@

\includegraphics{../../../../../../tmp/RtmpmEQua5/file9cb864dc16ed.png}

@@

\hypertarget{EG_modify_brlen}{%
\section{Changing branch length when reaching n taxa}\label{EG_modify_brlen}}
